---
title: "Boston Real Estate"
author: "Ke Li"
date: "March 1, 2016"
output: 
  html_document: 
    keep_md: yes
---
## Read in the dataset
```{r}
boston = read.csv("DataSets/boston.csv")
str(boston)
```
  + Per capita crime rate
  + Proportion of area used for industry
  + census track
  + concentration of Nitrious Oxides in the air
  + average rooms per dwelling
  + proportion of owner-occupied units built before 1940
  + how far the tract is from center of employment in Boston
  + is measure of closeness to important highways
  + property tax rate per $10,000 of value
  + pupil-teacher ratio by town
  
  ...

## Exploratary Data Analaysis - Geography

```{r}
# Boston Map Reflection
plot(boston$LON, boston$LAT)
# Charles River
points(boston$LON[boston$CHAS==1], boston$LAT[boston$CHAS==1], col="blue", pch=19)
# MIT
points(boston$LON[boston$TRACT==3531], boston$LAT[boston$TRACT==3531], col="red", pch=19)
# Watertown, my house
points(boston$LON[boston$TRACT==3701], boston$LAT[boston$TRACT==3701], col="green", pch=19)
```

## Air Pollution
```{r}
summary(boston$NOX)
```
```{r}
# Boston Map Reflection
plot(boston$LON, boston$LAT)
# NOX concentration
points(boston$LON[boston$NOX>0.53], boston$LAT[boston$NOX>0.53], col="grey", pch=19)
```

## Housing Price
```{r}
summary(boston$MEDV)
```
```{r}
# Boston Map Reflection
plot(boston$LON, boston$LAT)
# NOX concentration
points(boston$LON[boston$MEDV>21.20], boston$LAT[boston$MEDV>21.20], col="blue", pch=19)
```

